\documentclass[12pt]{article}

\begin{document}

{\huge Questions for interviews} 
 
Type 1: information about the interviewee and knowledge about the survey(this would take about 4-5 mins)

profession/education background/explanation of the topic, give examples if the interviewee is not clear with what a TF is/inform about the privacy issue(what it will be used for)

Type 2: Background/history related to usage, basic questions

1.Do you know about transcendental functions? (this may be combined with the procedure in Q0)
Do you use transcendental functions in daily life?
(Or) Have you ever? Now? Get in touch with?

2.In what cases do/did you use it?(If the interviewee mentions what function he/she used, q1 in type3 can be ignored)
 
3.What tools do you use to calculate?

4.(pending)If it is not a calculator, does anyone recommend for him/her or the interviewee searched online and randomly picked one? (May or may not be a question)

5.frequency-how often do you calculate TF?

Type 3: The need of the user

1.What transcendental functions did you use?
2.What is the preferable precision for you (decimals like 0.xxxxxx)
3. What is the preferable interface for you? (textual, graphical)(here or user experience)
 
Type 4: User experience
1.Do you find it easy to use?(maybe a rating question from 0-5?if 0-3, ask what needed to be improved?)
2.(Is a manual necessary?)

3.Can you recall how long does it take to get the result? Are you satisfied with that?

4.What are the issues or the problems that you had while using a calculator?
(I think “Is there any” is perferable)(Possible that No.6 is mentioned)

5.What are your solutions to solve those problems?

6.Do you think the functions that calculator provided fulfills your need? (If not, what should be improved?)
 
7.Are you willing to turn to a specific designed tool for calculating if it fulfills all your needs?
 

Type 5: questions that I cannot classify XD

1.Anyone else you know have the need of using it? Have you heard about their opinion?
  
6.
How important is a visual interface (GUI) to you when using a calculator?

7.1

What functions of a calculator do you use the most?

7.2

What functions of a calculator do you use the least?

8. 

Do you have a computer at work or at home while you need a calculator?

8.1

Are you familiar with command line application or programming?  (User must be able to use the Java application and command line)

8.2

Are you willing to use a calculator application on a computer?

8.3

Do you agree that a scientific calculator should output the result as many digits as possible in terms of irrational numbers?

1.Disagree  2. Dont care 3. Agree 4. IDK

8.4

Do you agree that a scientific calculator should take multiple inputs at once; in other words, is it better to take a function as input?

1.Disagree  2. Dont care 3. Agree 4. IDK



\end{document}